Asymmetric relationships and their effects on coexistence

### 2023-07-20 paper/RefereeResponses1.tex

\noindent C22) L74: The optimum might actually be the same, but they need different responses. \\

\noindent ***\emph{Thanks for pointing this out, we have corrected our language.} \\
%DONE

\noindent C23) Eq. 1: I would not use any equations in the introduction, and in general this part of the introduction did not feel like an introduction at all and might require a different sub-section \\

\noindent ***\emph{We disagree, and would prefer not to make this change, for several reasons. 
First, the lottery model is a very simple model, at the same level of complexity
as models introduced in essentially all introductory 
undergraduate ecology courses (e.g., the Lotka-Volterra competition model), so there is no argument that 
the readership of Ecology Letters cannot easily understand the material presented here.
Second, this material serves a clear motivating purpose, most appropriately placed in the Introduction. 
The last author (DCR) has found, from decades of pitching 
quantitative papers to general ecological audiences, that clear motivation is essential - it is crucial to demonstrate 
clearly that an effect one plans to elaborate is present, and potentially important, prior to asking the reader to engage 
the kind of mental energy necessary to read the guts of the paper. So this 
paragraph is for showing that the effect of ATAs on coexistence can be real, at least for a simple 
example. That goal is convincingly 
accomplished by the paragraph, more so than could be accomplished by a purely qualitative, words-only Introduction. 
Given that the math is simple, and also more precise and definitive than 
qualitative verbal arguments, we think this material is actually
more beneficial to the readership and more effective for the intended motivational purpose than would be more words
(and we see based on C25 below that the referee appears to agree with us here in some respects, at least). 
Third, quantitative approaches are central in ecology these days, and increasingly so. The automatic tendency
to want to exclude mathematics of any kind from the Introduction, especially when the math is simple,
accessible, and serves a clear motivational purpose, seems like a dated bias to us. 
Finally, we firmly believe that ecology as a discipline gets stronger as it continues the clear
trend of the last few decades of incorporating more quantitative approaches. We believe we
benefit the field by challenging assumptions and biases such as categorically not putting equations 
in the Introduction.} \\
%Jasmin to read the above and let Dan know if it's convincing or not, and how it can be improved.
%It's done except for any improvements or revisions that Jasmin may suggest.
%Jasmin: I really like this response and don't think its too harsh or needs to be toned down.

@@

\noindent C26) L126: Do you do this in the appendix? \\

\noindent ***\emph{No. We can see how it would be done, but we have not formalized the mathematics. 
To avoid making claims that we have not fully supported
with rigorous mathematics, we rephrased to say the iid assumption is 
``probably not necessary''. Thanks for spurring us to do this.} \\
%DONE

\noindent C27) Eq 2.: I thought we also have to remove the effect of C varying alone and E varying alone? Is this included in the $\#$ term automatically? \\

\noindent ***\emph{No, the equation is correct as is. Please see equation 10 and related equations of 
Ellner et al, 2019, Ecology Letters. Yes, the effects of $C$ and $E$ varying are included in 
the $\#$ term because that terms involves both of them varying (though independently).

Also, see S3 "Mechanisms other than storage effect" of our Supporting information. 
%can delete if not needed
Since,
\begin{align}
\olep_i^{EC} &= \E[r_i(E_i,C_{i \bs i})]-\olep_i^E-\olep_i^C-\epsilon_i^0 \\
&= \olr_{i \bs i} - \olep_i^E - \olep_i^C - \epsilon_i^0,
\end{align}
and 
\begin{equation}
\olep_i^{(E\shp C)}=\E[r_i(E_i^\shp,C^\shp_{i \bs i})]-\olep_i^E-\olep_i^C-\epsilon_i^0
&= \olrs_{i \bs i} - \olep_i^E - \olep_i^C - \epsilon_i^0,
\end{equation}
then,
\begin{align}
\olep_i^{(EC)} = \olep_i^{EC}-\olep_i^{(E\shp C)}
&= (\olr_{i \bs i} - \olep_i^E - \olep_i^C - \epsilon_i^0) - (\olrs_{i \bs i} - \olep_i^E - \olep_i^C - \epsilon_i^0)
&= \olr_{i \bs i} - \olep_i^E - \olep_i^C - \epsilon_i^0 - \olrs_{i \bs i} + \olep_i^E + \olep_i^C + \epsilon_i^0
&= \olr_{i \bs i} - \olrs_{i \bs i}. 
\end{align}
So,
\begin{align}
\Delta_i^{(EC)}=\olep_i^{(EC)} - q_{ij}\olep_j^{(EC)}
&= (\olr_{i \bs i} - \olrs_{i \bs i}) - q_{ij}(\olr_{j \bs i} - \olrs_{j \bs i})
&= \olr_{i \bs i} - \olrs_{i \bs i} - q_{ij}\olr_{j \bs i} + q_{ij}\olrs_{j \bs i}
&= \olr_{i \bs i} - q_{ij}\olr_{j \bs i} - \olrs_{i \bs i} + q_{ij}\olrs_{j \bs i}
&= (\olr_{i \bs i} - q_{ij}\olr_{j \bs i}) - (\olrs_{i \bs i} - q_{ij}\olrs_{j \bs i}).
\end{align}
} \\
%Jasmin to check and make sure Dan is right , here. Maybe there is a better place to refer them to to support our claim?

### 2023-07-20 paper/Paper.Rnw
responding to C27 and C21

%Intro to competition, coexistence, MCT, etc.
Competition, coexistence, and the maintenance of biodiversity are research topics at the core of modern ecology 
\citep{MacArthur_1958, Hutchinson_1961, Schmida_1984}. The competitive exclusion principle states 
that two species competing for the same limiting resource cannot coexist at constant densities - one will 
instead outcompete the other and drive it extinct \citep{Hardin_1960}.
Modern coexistence theory [MCT; \cite{Chesson_1994,Chesson_2000,Barabas_2018}] is a 
framework for understanding how species nevertheless coexist, and biodiversity is maintained, in real ecosystems,
through the niche partitioning effects of environmental variation.
MCT breaks down coexistence into the contributions of various mechanisms, with names such as ``storage effects'' \citep{Chesson_1994} which will be familiar to some readers (storage effects are also reviewed conceptually below and 
defined formally in Theory). MCT has been
applied to several systems, including annual \citep{Angert_2009, Hallett_2019} and perennial plants \citep{Adler_2006, Adler_2010}, 
tropical trees \citep{Usinowicz_2012}, plankton \citep{Caceres_1997, Descamps_2005, Narawani_2013}, and corals \citep{Alvarez-Noriega_2020}. 
Although MCT is somewhat mathematically complex, recent extensions make it more accessible \citep{Ellner_2016,Ellner_2019}.

>>>>

%Intro to competition, coexistence, MCT, etc.
Competition, coexistence, and the maintenance of biodiversity are research topics at the core of modern ecology 
\citep{MacArthur_1958, Hutchinson_1961, Schmida_1984}. The competitive exclusion principle states 
that two species competing for the same limiting resource cannot coexist at constant densities - one will 
instead outcompete the other and drive it extinct \citep{Hardin_1960}.
Modern coexistence theory [MCT; \cite{Chesson_1994,Chesson_2000,Barabas_2018}] is a 
framework for understanding how species nevertheless coexist, and biodiversity is maintained, in real ecosystems,
through the niche partitioning effects of environmental variation.
MCT breaks down coexistence into the contributions of various mechanisms, with names such as ``storage effects'' \citep{Chesson_1994} which will be familiar to some readers (storage effects are also reviewed conceptually below and 
defined formally in Theory). MCT has been
applied to several systems, including annual \citep{Angert_2009, Hallett_2019} and perennial plants \citep{Adler_2006, Adler_2010}, 
tropical trees \citep{Usinowicz_2012}, plankton \citep{Caceres_1997, Descamps_2005, Letten2018}, and corals \citep{Alvarez-Noriega_2020}. 
%Narawani_2013
Although MCT is somewhat mathematically complex, recent extensions make it more accessible \citep{Ellner_2016,Ellner_2019}.
